---
title: "Bootstrapping"
author: "issa fall"
date: "November 14, 2015"
output: html_document
---
##loading data
```{r loading,echo=TRUE}
library(datasets)
data("mtcars")
str(mtcars)
summary(mtcars)
```
##bootstrapping a sigle statistic(k = 1)
The following generate the bootstrapped 95% CI for R-squared in the linear regression of miles per gallon(mpg)
on car weight(wt) and displacement(disp).The data source is mtcars.The bootstrapped confidence interval is 
based on 1000 replications.
```{r single statistic,echo=TRUE}
library(boot)
rsq<-function(formula, data, indices){
  d<-data[indices, ] # Allows boot to select sample
  fit<-lm(formula,data = d)
  return(summary(fit)$r.square) # Function to obtain R-square from data
  
}

results<-boot(data = mtcars,statistic = rsq, R = 1000, formula = mpg ~  wt+disp) # bootstrapping with 1000 replications
results
plot(results) # View results
boot.ci(results, type = "bca") # Get 95% CI
```

##bootstrapping several statistics(k > 1):bootstrap 95% CI for regression coefficients
```{r bootsrapping,echo=TRUE}
library(boot)
#Function to obtain regression weights
bs<-function(formula,data,indices){
  
  d<-data[indices, ]  #allows boot select sample
  
  fit<-lm(formula, data = d)
  
  return(coef(fit))
}
```
##View results
```{r results,echo=TRUE}
results<-boot(data = mtcars, statistic = bs, R = 1000, formula = mpg ~ wt+disp)
results
plot(results, indices =1) # intercept
plot(results, indices =2) # wt
plot(results, indices =3) # disp
```
##get 95% confidence intervals
```{r confidence interval,echo=TRUE}
boot.ci(results, type = "bca", index = 1) # intercept
boot.ci(results, type = "bca", index = 2) # wt
boot.ci(results, type = "bca", index = 3) # disp
```

