---
output: html_document
---
title:"Exponentials"
author: "issa fall"
date: "September 7, 2015"
```
  keep_md:true
```


          DISTRIBUTION OF THE MEANS OF 40 EXPONENTIALS
          
INTRODUCTION

We investigate the distribution of exponentials in R and compare it with the central limit
theorem.
The mean is 1/lambda
The standard deviation is also 1/lambda set to 0.2 for all the simulations.
It investigates the distribution of average of 40 exponentials.

##                                           SIMULATIONS
##Lambda
```{r lambda,echo=TRUE}
lambda =0.2
```
##Number of exponentials
```{r 40 exponentials,echo=TRUE}
n =40
```
##Number of simulations
```{r 1000 simulations to run,echo=TRUE}
nsims =1:1000
```
##Set the seed
```{r set a seed to reproduce the data,echo=TRUE}
set.seed(820)
means<-data.frame(x =sapply(nsims, function(x){
                      mean(rexp(n,lambda))}))
head(means)
```
##The sample mean
```{r sample mean,echo=TRUE}
mean(means$x)
```
##Confidence intervals
```{r confidence intervals ,echo=TRUE}
quantile(mean(means$x), c(0.025, 0.975))
```
##The theoretical mean
```{r theoretical mean,echo=TRUE}
1/lambda
```
##CONCLUSION

The sample mean and the theoretical mean are almost the same.

##The sample variance
```{r sample variance,echo=TRUE}
var(means$x)
```
##Confidence interval
```{r confidence intervals,echo=TRUE}
quantile(var(means$x), c(0.025, 0.975))
```
##Theoretical variance
```{r,echo=TRUE}
((1/lambda)/sqrt(40))^2
```
The variance of the sample and the theoretical variance are almost the same.
Let's show that the distribution is approimately normal.
##Let's upload ggplot2
```{r histogram,echo=TRUE}
library(ggplot2)
ggplot(data = means,aes(x = means))+geom_histogram(color ="black",fill ="lightblue",binwidth = 0.05)
```


##Loading Tooth Growth
```{r loading,echo=TRUE}
library(datasets)
data("ToothGrowth")
names(ToothGrowth)
head(ToothGrowth)
tail(ToothGrowth)
str(ToothGrowth)
summary(ToothGrowth)
with(ToothGrowth,plot(dose,len))
with(subset(ToothGrowth, supp =="OJ"),points(dose,len, col ="blue"))
boxplot(len ~ supp,ToothGrowth,xlab ="supp",ylab ="len", main = "ToothGrowth")
fit<-lm(len ~., data = ToothGrowth)
summary(fit)$coef
table(ToothGrowth$supp)
oj<-subset(ToothGrowth, supp == "OJ")
head(oj)
hist(oj$len, col = "red")
vc<-subset(ToothGrowth, supp == "VC")
head(vc)
hist(vc$len, col = "red")
qq<-qplot(dose, len, colour = supp, data = ToothGrowth)
qq + geom_smooth(method = "lm", formula = y ~ x)
```


##Bootstrapping the statistics(dose) at a 95% CI
```{r bootstrapping,echo=TRUE}
library(boot)
```
##Function to obtain regression coef
```{r,echo=TRUE}
bs<-function(formula, data, indices){
  
  d<-data[indices, ] # allow boot to select sample
  
  fit<-lm(formula, data = d)
  return(coef(fit))
}
```
##Bootstrapping with 1000 replications
```{r replications, echo=TRUE}
results<-boot(data = ToothGrowth, statistic = bs, R = 1000, formula = len ~.)
```
##View results
```{r results,echo=TRUE}
plot(results, index =1) # intercept
plot(results, index =2) #
plot(results, index =3)
```


##Get the 95% CI
```{r,echo=TRUE}
boot.ci(results, type = "bca", index = 1)
boot.ci(results, type = "bca", index = 2)
boot.ci(results, type = "bca", index = 3)


